\leavevmode%
\begin{center}
    \Large\bfseries\sffamily Declaration 
\end{center}

\noindent I declare that this dissertation represents an original report of my own work, has been written by myself and has not been previously submitted to the University of Edinburgh or to any other institution for a degree, diploma or other qualifications. Appropriate credit has been given within the dissertation where references are made to the work of others.

\vspace{20pt}

\begin{center}
    \Large\bfseries\sffamily Acknowledgements
\end{center}    

\noindent Raphael Chen would like to express his sincere appreciation to his primary supervisors (Dr. Timm \textsc{Krueger} and Dr. Qi \textsc{Zhou}) for the ongoing generous support, insightful guidance and constructive discussions throughout the entire duration of the research project. It was their continuous encouragement and great patience that positively influenced him to keep preserving and not give up especially through challenging periods. In addition, he is deeply grateful to both of them who have given numerous valuable advice and taught him the importance of conciseness. He would also like to thank his secondary supervisor Dr. Gail \textsc{Duursma}, who gave genuinely useful advice at the beginning of the research project and provided constructive feedback during the poster session. Finally, and most importantly, he would like to thank his family for all their unconditional love and support which motivated him to embrace his failures and keep moving forward in life.  